\section{Project Management}
For a project of this size, involving multiple people, a structured approach to organising how development of the project occurred was required

\subsection{Communication}
An important aspect of any project is communication between all parties involved. For this project, this included ourselves, but also our project supervisors.

Once a week we met with our project supervisors to discuss progress made from the previous meeting, and how progress would develop during the next week. These meetings also served as platform to display results of development of some aspects of the project, and directions for research in these areas could be suggested. Minutes from meetings can be found in Appendix \ref{sec:minutes}.

A single group email account was created: \href{mailto:warwicksna@gmail.com}{warwicksna@gmail.com}. This allowed members of the group, and our supervisors, to quickly contact each member of the group as any emails sent to this account were forwarded to all group members.

During the Easter vacation, the group continued the weekly meetings, without direct communication with our supervisors, using Google+ Hangouts. Google+ Hangouts provided an online system where each member of the group could join a chatroom style environment to discuss project development use voice and/or video communications. These meetings within the holiday were followed up with a summary email to the group email account and our project supervisors to ensure that anyone unavailable to make the meeting could be informed of what had been discussed.

\subsection{Group Management}
Each member within the group had a defined role for the development of the project as explained below:

\paragraph{James Michael}


\paragraph{James Kettle}
This member, in addition with Isaac Lewis, was involved with the design and implementation of the SOAP server and client.

This member also implemented scripts which used the Twitter API to collect data on users related to the EDL and UAF, and process the results into the \verb/graphml/ format.

\paragraph{Matthew Cranham}
This member of the group was involved with the design and implementation of the majority of the algorithms running on the cluster. 

This member also became responsible for maintaining the Hadoop cluster to ensure that it performed correctly. One serious issue which occurred with the cluster was that algorithms implemented using the Apache Giraph library would not run, which was fixed through editing a networking configuration file on each machine within the cluster.

Following the implementation of the algorithms and the acquisition of data, it fell to this member to perform analysis on multiple datasets to investigate not only the structure and properties of these datasets, but also the tool developed as an environment to perform analysis of large social networks.

\paragraph{Isaac Lewis}
This member, in addition to James Kettle, was involved in designing and implementing the SOAP server and SOAP client. They also had a role in implementing influence propagation algorithms to execute on the cluster.

\paragraph{Simon Burns}
This member of the group worked on further developing the user interface developed by last year's group. This involved attempting to making the visualisation component of the user interface a stand-alone component so that it could be reused for this project to visualise networks being analysed on the cluster.