\chapter{Motivation}

\section{Why Is This Important?}
Crimes are frequently committed by a network of individuals, be they loose-knit,
tight-knit, grassroots clusters or hierarchical supply chains. Aspects of the
relationships and power structures that compose these networks are betrayed in
the resulting address books and digital social networks, which the police can
frequently gain access to. However, this information has been distorted,
flattened; a deep relationship may appear as a series of unrelated entries in an
addressbook. While direct detective-work is invaluable for making these
connections, the ever-increasing quantity of data to be processed is rendering
this approach less effective . By modelling these networks as graphs, and
through the application of various algorithms, we can attempt to recover some of
this lost data. This will provide information about both individual users and
the overall network; cluster identification may detect distinct groups within a
single network and the influence and centrality of individual people can
likewise be calculated. At its simplest this information could help inform
decisions on which people the police should focus their resources on
apprehending, and where in the network to introduce undercover agents to
maximise their influence. 

\subsection{Scale}
Owing to the computational complexity of these algorithms, existing tools have
serious scalability issues. The advent of social networking sites has led to
sprawling networks with vast quantities of low-grade information that needs to
be heavily processed to extract anything of value. We have tackled this by
distributing the workload across clusters. Clusters are networks of computers
typically built with commodity-grade components, rendering them cheap and
scalable.
+some more on clusters

\subsection{Relevance}
Lacking access to any police datasets we chose to use publicly available data
from the `microblogging' site Twitter. Twitter is used by two groups the police
are interested in; the `English Defence League' (EDL) and `Unite Against Facism'
(UAF). Previous projects used Enron's emails. Times have changed since then;
emails only make up a fraction of a user's interactions and social networks have
a far higher degree. We demonstrate these techniques on modern, relevant
networks.

\begin{description}
\item[Advantage] poor operational security
\item[Disadvantage] HBGary / Anonymous
\end{description}

\subsection{Alternative Applications: Marketing}
Modelling influence manipulation and the like is also a core requirement of
`viral' marketing; marketers want to choose the ideal starting point in a
network to achieve maximum saturation. At its purest, the website
http://sponsoredtweets.com allows advertises to pay a set amount for a tweet
from a particular user and influence propagation can be used to inform decisions
about whether a well-connected root is worth the money. 

\subsection{Alternative applications: Persona Management}
This won't just aid manual infiltration by undercover agents; once it is
automated to a suitable degree it may be combined with `persona management
systems'; software that enables a single operator to control large numbers of
fake online identities, massively increasing their voice and influence over
discussions. Manual identification of influence relationships simply doesn't
scale to this level.
http://www.faqs.org/patents/app/20090313274

\begin{itemize}
\item specific example use-case
\end{itemize}
% \input{./tex/res_hadoop}

