\chapter{Research}
This chapter is composed of three sections. The first concerns itself with existing research within the area of the analysis of social networks. The second . The final section is concerned with distributed computing, and how it can be used for analysing graphs of social networks.

% Since we have a few distinct sections on this area, I think it's a good idea to split this into multiple smaller files as well

\section{Social Network Analysis}
Analysis of social networks is becoming ever-increasing in importance, with the huge growth social network sites such as Facebook\footnote{\url{https://www.facebook.com/}} and Twitter\footnote{\url{http://twitter.com/}} have experienced in recent years. This research undertaken within this section relates to various metrics which can be applied to a social network to identify important people within the network, and also how the structure of the network can be identified.

\input{./tex/res_comdetection}
\input{./tex/res_clusteringcoeffs}
\input{./tex/res_centrality}
\input{./tex/res_infprop}
\input{./tex/res_influence_manip}
\input{./tex/res_emergent_behaviour}

\section{Distributed Computing}
With the huge sizes social networks can reach, there needs to be efficient approaches to decrease the running time of algorithms for analysis of the networks. One approach is to use distributed computing to parallelise these algorithms, so that computation across the network occurs at the same time, where possible, and as such should reduce the running time of these algorithms.

One area of distributed computing which has been growing in recently is the use of the MapReduce framework developed by Google, and the free implementation by Apache of MapReduce, Hadoop. We will be looking to use Hadoop as an approach to parallelise algorithms for social network analysis.

This should achieve a reduced running time for algorithms, and also allow analysis of far larger networks than previously possible due to the scalability of the Hadoop framework.

\input{./tex/res_hadoop}
\input{./tex/res_giraph}
